# About

<!--
2024-01-22, Brad:
Ebie and I met this morning. We are planning to add a bunch of basic "About" information about DETECT to the homepage. We are leaving this separate "About" page for now, but I'm thinking we will end up dropping after we complete the homepage. It's possible that we will want a page about using this repository or the data tables (as opposed to "about DETECT" itself), but I think we will probably just use the repo's wiki for that.
-->

This is all copied from the Link2Care master table repo. Figure out if we want to do something similar for this project too.

```{r}
#| label: setup-about
#| echo: false

# Import the data that will be used to create the tables.
# Import `combined_participant_data.rds`. This dataset is created in `link2care_public/data_survey_21_merge.Rmd`. Additionally, this code assumes that this file is being run from the SharePoint `General` folder.

# Use `source("R/import_data.R")` to import the data at the top of every .qmd file. That way, the information in Administrative Information table on the home page is correct for all tables.
# source("R/import_data.R")

# Update: I moved source("R/import_data.R") to an .Rprofile file. That way, the file only runs once, rather than at the beginning of each qmd file. If this approach continues to work, then I will erase the notes above. 
```

::: callout-warning
The information on this page is not likely to be useful to many users. Rather, this page is intended to assist with site maintenance.
:::

# Overview of the data

The data for these tables is currently housed at UTHealth-Houston on the [DETECT SharePoint site](https://uthtmc.sharepoint.com/sites/SPHDETECT-RPC/SitePages/Home.aspx). Contact Brad Cannell at [Michael.B.Cannell\@uth.tmc.edu](mailto:Michael.B.Cannell@uth.tmc.edu) if you have questions about accessing the data.

Add some other stuff as it becomes relevant...

# Administrative information about the data

Currently, the code in this section is copied directly from the Link2Care master table repo. We will need to update it later if we are going to use it for this project too.

```{r}
#| label: table-administrative
#| echo: false
#| eval: false

# Turn numeric values into character strings for the table 
today <- as.character(Sys.Date())
rows <- as.character(df_dim[1])
columns <- as.character(df_dim[2])
n_overall <- as.character(n_participants) 
n_ucm <- as.character(n_per_group["UCM"])
n_ucmsp <- as.character(n_per_group["UCM+SP"])
n_l2c <- as.character(n_per_group["L2C"])

admin_info <- tibble::tribble(
  ~Attribute,                  ~Value,    ~Description,
  "Last updated:",             today,     "The date the tables on this website were last updated.",
  "Source data:",              df_nm,     "The name of the dataset used to create the tables on this website.",
  "Source data path:",         folder,    "The path to the source data.",
  "Source data size:",         df_size,   "The size of the modified data used to create the tables on this website.",
  "Source data row count:",    rows,      "The number of rows currently contained in the data used to create the tables on this website.",
  "Source data column count:", columns,   "The number of columns/variables currently contained in the data used to create the tables on this website.",
  "N participants:",           n_overall, "The number of unique participants in the data used to create the tables on this website.",
  "N UCM participants:",       n_ucm,     "The number of unique participants in the data who were in the usual care management arm of the Link2Care study.",
  "N UCM+SP participants:",    n_ucmsp,   "The number of unique participants in the data who were in the usual care management plus smart phone arm of the Link2Care study.",
  "N L2C participants:",       n_l2c,     "The number of unique participants in the data who were in the Link2Care arm of the Link2Care study."
)

knitr::kable(admin_info, align = c("l", "c", "c"))
```

# Codebook

The codebooks for the source data are available at: <https://github.com/brad-cannell/detect_fu_interviews_public/tree/main/codebooks>.

We may want to improve the links to the codebooks in the future.
