---
always_allow_html: yes
---

# Interviewer Observations
This page contains tables that summarize interviewer observations data for the DETECT F/U Interviews participants. Data for all follow-up visits is included even if a participant was visited more than once.

```{r}
#| include: false

library(dplyr, warn.conflicts = FALSE)
library(haven)
library(freqtables)
library(flextable)
library(officer)
library(knitr)


# Import the data that will be used to create the tables.
detect_fu_merge  <- readRDS("../data/cleaned_rds_files/detect_fu_data_merged.rds")

# Import dataframe containing description of variables
obs_desc <- readRDS("../sections/variable_descriptions/observational_measures_var_desc.rds")

# Import functions that will be used to calculate statistics
# Overall - Continuous columns
source("../R/n_mean_ci.R")
source("../R/n_median_ci.R")
source("../R/cont_stats.R")

# Overall - Categorical columns
source("../R/n_percent_ci.R")

# By group - Continuous columns
source("../R/n_mean_ci_grouped.R")
source("../R/n_median_ci_grouped.R")
source("../R/cont_stats_grouped.R")

# By group - Categorical columns
source("../R/n_percent_ci_grouped.R")

# Import function that will filter out the df from the merged df
source("../R/extract_df_from_merged_detect.R")
```

<!-- ## Create a data set with only the first visit for each unique person -->

```{r}
#| echo: false
# Extract the relevant df from the merged data frame
obs <- filter_merged_df(detect_fu_merge, "_obs")

```

<!-- ## Create lists of columns to analyze -->

```{r}
#| echo: false
# Create list of the names of the factor columns

obs_cols <- obs %>% select(ends_with("_f")) %>% select(order(colnames(.))) %>% names()
```


<!-- ## Create data frame that contains overall summary statistics for the data -->

```{r}
#| echo: false
# add categorical variables to list

obs_stats_list <- obs_cols |>
  rlang::set_names(obs_cols) |> 
  purrr::map(~ n_percent_ci(obs, !! rlang::sym(.x), 1))

```

```{r}
#| echo: false

obs_table <- purrr::map_dfr(
  # Bind the list items together as rows
  .x = obs_cols,
  .f = ~ dplyr::bind_rows(obs_stats_list[[.x]])
)

# Reorder the columns so that `cat` comes after `var`
obs_table <- obs_table |> 
  dplyr::select(everything())

# Add description column 
obs_table <- obs_table %>%
  left_join(., obs_desc, by = c("var" = "name"))
```

```{r}
#| echo: false
# Split data frame into list of data frames by variable
obs_table_list <- split(obs_table, obs_table$var)

```


<!-- ## Create Flextables -->

## Tables

### Categorical Variables
```{r, include = FALSE}
cat_flextable <- function(var_name, table_list = obs_table_list) {
  # Extract each variable data frame from list 
  df <- data.frame(table_list[[var_name]])
  
  # Set up table header line text including variable name and description
  title_cap <- as_paragraph(var_name)
  desc_cap <- df %>% select(description) %>% unique() %>% toString() %>% as_paragraph()
    
    # Create flextable
    flex_tab <- flextable(df, col_keys = c("var", "cat", "n", "formatted_stats")) %>%
      # Rename columns
      set_header_labels(
        var = "Variable", 
        cat = "Category", 
        "n" = "N",
        "formatted_stats" = "Percent of N (95% CI)") %>%
      
      # Format Header lines
      add_header_lines(desc_cap) %>%
      add_header_lines(title_cap) %>%
      bg(bg = "transparent", part = "header", i = c(1,2)) %>%
      align(align = "left", part = "header") %>%
      
      # Shade alternating rows using zebra theme
      theme_zebra(
        odd_header = "transparent",
        odd_body = "transparent",
        even_header = "transparent",
        even_body = "#f1f1f1"
      ) %>%
      
      # Add border lines to header and format header
      border(i = 3, part = "header", border.top = fp_border(color = "black"), border.bottom = fp_border(color = "black")) %>%
      bold(i = c(2,3), part = "header", bold = FALSE) %>%
      
      # Set width and alignment
      width(j = c(1,2,3,4), width = c(2.4, 2.6, 1, 2), unit = "in") %>%
      align(align = "left", part = "all") %>%
      # Add space for website view
      add_footer_lines("")
    
    flex_tab
}
```


```{r, results ='asis', echo=FALSE}
flextables <- lapply(obs_cols, cat_flextable)

for (x in 1:length(obs_cols)) {
  cat(knit_print(flextables[[x]]))
  }

```


<!-- ## Create table containing descriptions for short answer variables.-->

### Free Text Variables

These variables contain free text response data that is not analyzed on this site.

```{r, include = FALSE}
free_res <- obs_desc %>% filter(grepl("_comments$", name) | grepl("at_.+_why", name)) 
```

```{r, echo = FALSE}
free_res_flex <- flextable(free_res) %>%
  # Rename columns
  set_header_labels(
    name = "Variable",
    description = "Description") %>%
  
  # Shade alternating rows using zebra theme
  theme_zebra(
    odd_header = "transparent",
    odd_body = "#f1f1f1",
    even_header = "transparent",
    even_body = "transparent"
  ) %>%
  
  # Set header alignment
  align(align = "left", part = "header") %>%
  
  # Set table width and alignment
  width(j = c(1,2), width = c(2,7), unit = 'in') %>%
  align(align = "left") 

free_res_flex
```


## Download Tables in Word File

```{r}
#| include: false

# Define title and subtitle styles
title_style <- fp_text_lite(font.size = 18, bold = TRUE)
subtitle_style <- fp_text_lite(font.size = 14, bold = TRUE, color = "#A7A7A7")


#  Create an empty Word document
obs_doc <- read_docx()


obs_doc <- obs_doc %>%
  
  # Add Headings
  body_add_fpar(fpar(ftext("Interviewer Observations", prop = title_style))) %>%
  body_add_par("")

# Add categorical variable tables into Word document
obs_doc <- obs_doc %>%
  
  # Add Headings
  body_add_fpar(fpar(ftext("Categorical Variables", prop = subtitle_style))) %>%
  body_add_par("") 

for (var_name in obs_cols) {
  cat_flex <- cat_flextable(var_name)
  # Set width of tables
  cat_flex <- cat_flex %>% width(j = c(1,2,3,4), width = c(2.3, 1.7, 0.8, 2), unit = "in") %>%
    # Remove space for document view
    delete_part(part = "footer") %>%
    # Prevent table breaking up into different pages.
    paginate(init = TRUE, hdr_ftr = TRUE)
  # Align tables and add a separating empty line between each table    
  obs_doc <- obs_doc %>%
    body_add_flextable(cat_flex, align = "left") %>%
    body_add_par("")
    
}

obs_doc <- obs_doc %>%
  body_add_break() %>%
  
  # Add Headings
  body_add_fpar(fpar(ftext("Free Text Variables", prop = subtitle_style))) %>%
  body_add_par("") %>%
  
  body_add_flextable(width(free_res_flex, j = c(1,2), width = c(2, 4.7)))

# print the word document
print(obs_doc, target = "../sections/observational_measures_tables.docx")
```


```{r}
#| label: download_docx
#| echo: false

downloadthis::download_file(
  path = "observational_measures_tables.docx",
  output_name = "Observational Measures Tables",
  button_label = "Download table",
  button_type = "success",
  has_icon = TRUE,
  icon = "fa fa-save"
)
```





