---
always_allow_html: yes
---

# Sociodemographic Information

This page contains tables that summarize sociodemographic data for the DETECT F/U Interviews participants. 


```{r}
#| label: sociodemographic-information-data-setup
#| include: false

library(dplyr, warn.conflicts = FALSE)
library(haven)
library(freqtables)
library(flextable)
library(officer)

# Import function that will be used to add shade to the table by variable name
source("../R/add_shade_column.R")

# Import the data that will be used to create the tables.
soc_dem  <- readRDS("../data/cleaned_rds_files/sociodemographic_information_import.rds")
participant <- readRDS("../data/cleaned_rds_files/participant_import.rds")

# Import functions that will be used to calculate statistics
# Overall - Continuous columns
source("../R/n_mean_ci.R")
source("../R/n_median_ci.R")
source("../R/cont_stats.R")

# Overall - Categorical columns
source("../R/n_percent_ci.R")

# By group - Continuous columns
source("../R/n_mean_ci_grouped.R")
source("../R/n_median_ci_grouped.R")
source("../R/cont_stats_grouped.R")

# By group - Categorical columns
source("../R/n_percent_ci_grouped.R")

# Import function that will create summary data sets of unique people and create a data set with only the first visit for each unique person
source("../R/unique_people.R")
```

<!-- # Analysis -->

<!-- ## Create a data set with only the first visit for each unique person -->

```{r}
#| echo: false

socio_demo_unique_list <- unique_people(soc_dem)

socio_demo <- socio_demo_unique_list$df_first_visit_only

```


<!-- ## Calculated variables -->

```{r}
#| echo: false
socio_demo <- socio_demo |>
  mutate(
   sode_race_8cat = case_when(
      is.na(sode_race)                                         ~ NA_integer_,
      sode_race == "American Indian or Alaskan Native"         ~ 1,
      sode_race == "Asian"                                     ~ 2,
      sode_race == "Black or African American"                 ~ 3,
      sode_race == "Native Hawaiian or Other Pacific Islander" ~ 4,
      sode_race == "White"                                     ~ 5,
      sode_race == "Don't know"                                ~ 7, 
      sode_race == "Refused"                                   ~ 8,  
      TRUE                                                     ~ 6  # "Other race or multiple races",
                                  
      
    ),
   sode_race_8cat_f = factor(
     sode_race_8cat, 
     levels = c(1,2,3,4,5,6, 7, 8),
     labels = c("American Indian or Alaskan Native","Asian", "Black or African American", "Native Hawaiian or Other Pacific Islander",
                "White", "Other race or multiple races", "Don't know", "Refused")
   ),
   sode_race_eth_6cat = case_when(
      is.na(sode_hispanic_4cat_f)                              ~ NA_integer_,
      sode_hispanic_4cat_f == "Yes"                            ~ 1, # "Hispanic, any race"
      sode_race == "Black or African American"                 ~ 2, # "Black, non-Hispanic"
      sode_race == "White"                                     ~ 3, # "White, non-Hispanic"
      sode_hispanic_4cat_f == "Don't know"                     ~ 5, 
      sode_hispanic_4cat_f == "Refused"                        ~ 6,                     
      TRUE                                                     ~ 4, # "Other race or multiple races, non-Hispanic"
    ),
   sode_race_eth_6cat_f = factor(
     sode_race_eth_6cat, 
     levels = c(1,2,3,4,5,6),
     labels = c("Hispanic, any race", "Black, non-Hispanic", "White, non-Hispanic", "Other race or multiple races, non-Hispanic", "Don't know", "Refused")
     ) 
   )
```

```{r}
#| echo: false
#| warning: false
socio_demo <- socio_demo |>
  mutate(
    sode_people_cont = case_when(
      sode_people == "Don't know"
      | is.na(sode_people)        ~ NA_integer_,
      TRUE                        ~ as.numeric(sode_people)
    )
  )
```

<!-- ## Create lists of columns to analyze -->

```{r}
#| label: socio-demo-define-cat-cols
#| echo: false

socio_demo_cat_cols <- c("sode_race_8cat_f", "sode_race_eth_6cat_f", "sode_marital_8cat_f", "sogi_identity_5cat_f", "sogi_orientation_8cat_f", "sode_hispanic_4cat_f", "sode_school_9cat_f", "sode_employed_11cat_f", "sode_income_9cat_f", "sode_military_4cat_f", "sode_unwanted_4cat_f", "sode_sexual_4cat_f", "hsi_contact_4cat_f")
```

```{r}
#| label: socio-demo-define-cont-cols
#| echo: false

socio_demo_cont_cols <- c("sode_age_years", "sode_people_cont")
```

<!-- ## Create a data frame that contains overall summary statistics -->

```{r}
#| label: socio-demo-add-cont-stats-list-overall
#| echo: false
socio_demo_stats_list <- socio_demo_cont_cols  |> 
  rlang::set_names(socio_demo_cont_cols) |> 
  purrr::map(~ n_mean_ci(socio_demo, !! rlang::sym(.x), 1))
```

```{r}
#| label: socio-demo-add-cat-stats-list-overall
#| echo: false
socio_demo_stats_list <- c(
  socio_demo_stats_list,
  socio_demo_cat_cols |>
    rlang::set_names(socio_demo_cat_cols) |> 
    purrr::map(~ n_percent_ci(socio_demo, !! rlang::sym(.x), 1))
)
```

<!-- ## Bind together the continuous and categorical summary stats -->

```{r}
#| label: socio-demo-stats-list-to-df-overall
#| echo: false
socio_demo_table <- purrr::map_dfr(
  
  # This is where we can set the order of the rows
  .x = c("sode_age_years", "sode_people_cont", "sode_race_8cat_f", "sode_race_eth_6cat_f", "sode_marital_8cat_f", "sogi_identity_5cat_f", "sogi_orientation_8cat_f", "sode_hispanic_4cat_f", "sode_school_9cat_f", "sode_employed_11cat_f", "sode_income_9cat_f", "sode_military_4cat_f", "sode_unwanted_4cat_f", "sode_sexual_4cat_f", "hsi_contact_4cat_f" ),
  .f = ~ dplyr::bind_rows(socio_demo_stats_list[[.x]])
)

# Reorder the columns so that `cat` comes after `var`
socio_demo_table <- socio_demo_table |> 
  dplyr::select(var, cat, everything())
```

<!-- Make a variable name key -->

## Variable Name Key

The following table provides a description for each variable that appears in the following tables of descriptive statistics.

```{r}
#| label: lead-panel-data-variable-name-key
#| echo: false

key <- tribble(
 ~var, ~description,
 "sode_age_years", "Participant's age in years",
 "sode_people_cont", "The number of people that live in the participant's household, including the participant",
 "sode_race_8cat_f", "The participant's self-reported race",
 "sode_race_eth_6cat_f", "The participant's self-reported race/ ethnicity collapsed into 4 categories",
 "sode_marital_8cat_f", "The participant's self-reported marital status",
 "sogi_identity_5cat_f", "The particpant's self-reported gender identity",
 "sogi_orientation_8cat_f", "The particpant's self-reported sexual orientation",
 "sode_hispanic_4cat_f", "Participant's self-report of Hispanic ethnicity", 
 "sode_school_9cat_f", "Participant's self-reported highest level of schooling completed",
 "sode_employed_11cat_f", "Participant's self-reported employment status",
 "sode_income_9cat_f", "Participant's self-reported total household income before taxes",
 "sode_military_4cat_f", "Whether or not the participant has ever served in the military",
 "sode_unwanted_4cat_f", "Whether or not the participant has ever received unwanted, threatening or repeated sexual attention during military service",
 "sode_sexual_4cat_f", "Whether or not the participant has ever had sexual contact against their will or when they were unable to say no during military service",
 "hsi_contact_4cat_f", "Whether or not the participant provided assent for future contact"
)

DT::datatable(
  key,
  colnames = c("Variable Name", "Variable Description")
)
```

## Unique People Summary Table

```{r}
#| echo: false

socio_demo_unique_table <- socio_demo_unique_list$df_unique_summary

DT::datatable(
  socio_demo_unique_table,
  colnames = c("", ""),
  escape = FALSE, # So the HTML superscript in the column header will work
  options = list(
    columnDefs = list(
      # Hide row numbers column from view
      list(targets = 0, visible = FALSE),
      # Center values
      list(className = 'dt-left', targets = 1:2),
      # Make first column bold
      list(className = 'dt-bold', targets = 1)
    )
  )
) |>
    DT::formatStyle(1,
    fontWeight = 'bold'
    )
```


## Overall Statistics for Only the First Visit for Each Person

```{r}
#| echo: false

# Add a column that we can use to shade every other var name.
socio_demo_table <- add_shade_column(socio_demo_table)


DT::datatable(
  socio_demo_table,
  colnames = c("Shade", "Variable", "Category", "N", "Statistic (95% CI)"),
  escape = FALSE, # So the HTML superscript in the column header will work
  options = list(
    pageLength = 20,
    columnDefs = list(
      # Center n and formatted stats
      list(className = 'dt-center', targets = 4:5),
      # Hide row numbers column from view
      list(targets = 0, visible = FALSE),
      # Hide "shade" column from view
      list(targets = 1, visible = FALSE)
    )
  )
) |> 
  DT::formatStyle(
    "shade",
    target = "row",
    backgroundColor = DT::styleEqual(c(0, 1), c('white', '#ededed'))
  )
```

```{r}
#| echo: false

# Create and format flextables that can be downloaded in Word document
socio_demo_flex <- flextable(socio_demo_table, 
                  col_keys = c("var", "cat", "n", "formatted_stats")
                  ) %>%
  # Set caption
  set_caption("Summary statistics for DETECT F/U Participants Sociodemographic Information Dataset") %>%
  
  # Alternatively shade each group
  bg(i = ~ shade == "FALSE", bg = "#ededed", part = "body") %>% 
  
  # Rename columns
  set_header_labels(
    var = "Variable", 
    cat = "Category", 
    "n" = "N",
    "formatted_stats" = "Statistic (95% CI)"
  )%>%
  
  # Format width of table
  width(width = 2)


```

## 🔴 Testing out downloading

Example from the [downloadthis website](https://fmmattioni.github.io/downloadthis/index.html). This works, but Excel isn't the most user-friendly format. 

Turn the `socio_demo_table` into a downloadable flextable object in a Word.

```{r}
#| echo: false
#  Create an empty Word document
soc_doc <- read_docx()

# Add tables to Word document
soc_doc <- soc_doc %>% 
  body_add_flextable(socio_demo_flex, align = "left")

# print the word document
print(soc_doc, target = "socio_demo_overall.docx")

```

```{r}
#| label: download_docx_example
#| echo: false
downloadthis::download_file(
  path = "socio_demo_overall.docx",
  output_name = "Sociodemographic Information Summary",
  button_label = "Download table",
  button_type = "success",
  has_icon = TRUE,
  icon = "fa fa-save"
)
```

